\documentclass{article}
\pagenumbering{gobble}

\usepackage[letterpaper,margin=1.5in]{geometry}

\begin{document}

\begin{center}
\section*{Biographical Sketch}

\subsection*{Steven Clontz}
\end{center}

\subsection*{a. Professional Preparation}

 \begin{tabular}{llll}
   Auburn University &
      Auburn, AL &
      Mathematics &
      B.S., 2008
      \\
   Auburn University &
      Auburn, AL &
      Mathematics &
      M.S., 2010
      \\
   Auburn University &
      Auburn, AL &
      Mathematics &
      Ph.D., 2015
      \\
 \end{tabular}

\subsection*{b. Appointments}

\begin{description}
  \item[2016--present:] \textbf{Assistant Professor}

  Univerity of South Alabama | Mobile, AL

  \item[2015--2016:] \textbf{Visiting Assistant Professor}

  University of North Carolina at Charlotte | Charlotte, NC
\end{description}



\subsection*{c. Products}


\subsubsection*{(i) Publications most closely related to the project.}
\begin{itemize}
  \item \textbf{Clontz, S.}
    \textit{Applications of limited information strategies in Menger's game.}
    Comment. Math. Univ. Carolin., to appear.
  \item \textbf{Clontz, S.} and Dow, A.
    \textit{Almost compatible functions and infinite-length games.}
    Rocky Mountain J. Math., to appear.
  \item \textbf{Clontz, S.}
    \textit{Relating games of Menger, countable fan-tightness, and selective separability.}
    In preparation.
\end{itemize}


\subsubsection*{(ii) Other important publications.}
\begin{itemize}

  \item \textbf{Clontz, S.} and Gruenhage, G.
    \textit{Proximal compact spaces are Corson compact.}
    Topology Appl. 173 (2014), 1-8.
  \item \textbf{Clontz, S.}
    \textit{Zero-Markov information in topological games.}
    Ala. J. Math. 39 (2015).
  \item \textbf{Clontz, S.}
    \textit{Tactic-proximal compact spaces are strong Eberlein compact.}
    Topology Appl. 204 (2016), 306-317.
  \item \textbf{Clontz, S.}
    \textit{On \(k\)-tactics for Gruenhage's compact-point game.}
    Q\&A in Gen. Topology 34 (2016), 1-10.
  \item \textbf{Clontz, S.} and Varagona, S.
    \textit{Destruction of metrizability in generalized inverse limits.}
    Top. Proc. 48 (2016), 289-297.


\end{itemize}

\subsection*{d. Synergistic Activities}

\begin{itemize}%[itemsep=4pt]

  \item Reviewer for Mathematical Reviews / MathSciNet.
  \item Maintainer of the Online Streams in Mathematics project, which
  provides support for streaming mathematical talks and lectures online
  using free open-source software.
  \item Lead Editor for pi-Base, an online encylopedic database of
  topological spaces, properties, and theorems.




\end{itemize}

\end{document}
