
%%%%%%%%% BIOGRAPHICAL SKETCH -- 2 pages
\vspace{-4\baselineskip}
\required{Biographical Sketch For Dr. Steven Clontz}

% Your Bio should be divided into the following sections
% (a) Professional Preparation (education):
% Undergrad, Major, Year
% Graduate, Major, Year
% Postdoc, Area, Years-Inclusive
% (b) Appointments:  most recent first.
% (c) Products:  5 related to the proposal, and 5 "Other Significant Publications"
% (d) Synergistic Activities (math-enhancing activities that were not
% part of your main job description, like editorial boards and
% conference organizing - any Math-related volunteer work.
% these are often similar to Broader Impacts

% (e) Collaborators & Other Affiliations: (use the following sections)
% list in alphabetical order, and include current affiliations parenthetically
% Collaborators and Co-editors: past 48 months.  If none, write "none"
% Graduate Advisors and Postdoctoral sponsors: (your own, no matter how long ago)
% Thesis advisor and postgraduate scholar-sponsor:  those you have advised
% in the past 5 years.
% Total number of graduate students advised: X (all time)
% Total number of postdoctoral scholars sponsored: Y (all time) \maketitle


\textbf{Address}

\noindent Department of Mathematics and Statistics \\
University of South Alabama, Mobile, AL 36688\\
(251) 460-6757\\
sclontz@southalabama.edu

\medskip

\medskip

\noindent\textbf{a. \medskip Professional Preparation}

 \noindent   Auburn University, Auburn, AL;
        Mathematics;
        B.S., 2008
        \\
     Auburn University, Auburn, AL;
        Mathematics;
        M.S., 2010
        \\
     Auburn University, Auburn, AL;
        Mathematics;
        Ph.D., 2015
        \\

\medskip

\noindent\textbf{b. \medskip Appointments}

\begin{description}%[label={\quad 9999--9999:},leftmargin=*,itemsep=0pt]
  \item[2016--present:] \textbf{Assistant Professor}, The Univerity of South Alabama, Mobile, AL
  \item[2015--2016:] \textbf{Visiting Assistant Professor}, The University of North Carolina at Charlotte, Charlotte, NC


\end{description}

\noindent\textbf{c. \medskip Products}


\noindent\textbf{(i) Five Publications most closely related to the project.}
\begin{itemize}%[itemsep=5pt]

  \item \textbf{Clontz, S.} and Gruenhage, G.
    \textit{Proximal compact spaces are Corson compact.}
    Topology Appl. 173 (2014), 1-8.
  \item \textbf{Clontz, S.}
    \textit{Zero-Markov information in topological games.}
    Ala. J. Math. 39 (2015).
  \item \textbf{Clontz, S.}
    \textit{Tactic-proximal compact spaces are strong Eberlein compact.}
    Topology Appl. 204 (2016), 306-317.
  \item \textbf{Clontz, S.}
    \textit{On \(k\)-tactics for Gruenhage's compact-point game.}
    Q\&A in Gen. Topology 34 (2016), 1-10.
  \item \textbf{Clontz, S.} and Varagona, S.
    \textit{Destruction of metrizability in generalized inverse limits.}
    Top. Proc. 48 (2016), 289-297.


\end{itemize}

\noindent\textbf{d. \medskip Synergistic Activities}

\begin{itemize}%[itemsep=4pt]

  \item Maintainer of the Online Streams in Mathematics project, which
  provides support for streaming mathematical talks and lectures online
  using free open-source software.
  \item Reviewer for Mathematical Reviews / MathSciNet.
  \item Founder and software engineer for Teloga.com, customer relationship
        management software-as-a-service for collegiate music organizations
        from 2011-2015.
  \item Director of Mathematical Puzzle Programs, an organization which
        organizes mathematical puzzle events to encourage young people to
        engage in mathematical problem-solving.
  \item Served the National Youth Leadership Training program at Camp Westmoreland,
        Florence, AL from 2002-2011 as director, quartermaster, and
        numerous other roles.




\end{itemize}

\noindent\textbf{e. \medskip Collaborators \& Other Affiliations}

\begin{itemize}

    \item \textbf{Collaborators and Co-Editors:}\\
        \begin{itemize}
          \item Gary Gruenhage (Auburn University)
          \item Scott Varagona (University of Montevallo)
          \item Alan Dow (UNC Charlotte)
        \end{itemize}

    \item \textbf{Graduate Advisers and Postdoctoral Sponsors:}\\
        \begin{itemize}
          \item Gary Gruenhage (PhD Advisor, Auburn University)
          \item Alan Dow (Mentor, UNC Charlotte)
        \end{itemize}


    \item \textbf{Thesis Adviser and Postgraduate-Scholar Sponsor:}\\
        Undergraduate thesis students: 1;
        Total graduate students: 0; Total postgraduate scholars: 0.


\end{itemize}
